Defending Against Web Application Attacks: Research Approaches, Challenges and Implications

### 2015-01-16 docs/rebuttal_merged.txt

We thank the reviewers for their insightful comments.

Some general points:

We didn't consider mechanisms that haven't been presented in research papers. We mention Caja due to its importance.

Although some of the presented works use static/dynamic analysis, we don't consider that area (another paper covers it [14]), but focus only on protections against attacks that exploit such vulnerabilities.

We'll update our paper to address the issues indicated by the the reviewers, i.e. the title, the point where language protection mechanisms detect an attack, the "ease of use" dimension, the SQLi example, the fact that we fail to capture PHP injection in our model and the model's 1/1.1 notation.

@@

Rev1:

Sensitivity and specificity should be more applicable, but not enough data is given in the publications (see VII.A). The usefulness of such metrics in computer security has been advocated by others, i.e. Pfleeger and Pfleeger (Analyzing Computer Security: A Threat/Vulnerability/Countermeasure Approach, Prentice Hall, 2011); we’ll add the citation.

There are too many N/As (especially in Table II), but this actually highlights the issues regarding code availability and accuracy testing.

We'll include FlowFox and JSand, the paper presenting IFC in WebKit's JavaScript Bytecode and discuss ADsafe etc. AdSentry, Contego, and JSFlow don't reach our citation threshold.

Using "security" as a dimension is misleading---we mean ease of circunvention, which is orthogonal to "accuracy". We'll replace it with a more specific term.

@@

We attempt to cover mechanisms and then highlight reasons why a mechanism may not be widely used. In the conclusions we mention that CSP is one of the few that has been published and is widely used. It is true that if programmers use secure coding practices like prepared statements, then SQLi protections aren't required. However, that may not happen, and this motivates proposals like SQLrand, which might be easier to retrofit in existing code bases.

Our model covers attacks that utilize DSL languages in general, and in our categorization there are more than one countermeasures that protect from XPathi.

Rev3:

Sensitivity and specificity could be expressed in terms of a conditional probability---we'll include this in the paper.

@@

The comment on the skewed data is valid. We don't know in the papers we studied if test data were skewed. We do find, though, that: more tests could have been performed (Table I and VII.A) and the means to conduct tests should be made available to third parties (Table II and VII.B).

Rev4:

We don't intend to criticize the lack of testing in etiological mechanisms. We attempt to explore why such mechanisms aren't widely used, and suggest that this is one reason.

About demanding prevalence: it may be unfair to ask of researchers to provide PPV and NPV values for their mechanisms. In p.13 we explore what this would require---we'll elaborate.

### 2015-01-16 docs/rebuttal_merged.txt

We thank the reviewers for their insightful comments.

General points:

We didn't consider mechanisms that haven't been presented in research papers. We mention Caja due to its importance.

Although some of the presented works use static/dynamic analysis, we don't consider the area of static/dynamic analysis for vulnerability detection (another paper covers it [14]), but focus only on protections against attacks that exploit such vulnerabilities.

We'll update our paper to address the issues indicated by the the reviewers, i.e. the title, the point where language-protection mechanisms detect an attack, the "ease-of-use" dimension, the SQLi example, the fact that we fail to capture PHP injection in our model and the model's 1/1.1 notation.

@@

Rev1:

Sensitivity and specificity should be more applicable, but not enough data is given in the publications (see VII.A). The usefulness of such metrics in computer security has been advocated by others, i.e. Pfleeger and Pfleeger in "Analyzing Computer Security: A Threat/Vulnerability/Countermeasure Approach"---we’ll add the citation.

@@

There are too many N/As (especially in Table II), but this actually highlights the issues regarding code availability and accuracy testing.

We'll include FlowFox and JSand, the paper presenting IFC in WebKit's JavaScript-Bytecode and discuss ADsafe etc. AdSentry, Contego, and JSFlow don't reach our citation threshold.

Using "security" as a dimension is indeed misleading---we mean ease-of-circumvention, which is orthogonal to "accuracy". We'll replace it with a more specific term.

@@

We'll enrich the security discussion. For instance, approaches that provide systematic arguments on why their designs are secure, cannot be circumvented like heuristic/threshold-based approaches.

Rev2:

The lack of code availability makes performing original tests challenging, which is one of our findings (VII.B).

We attempt to cover mechanisms and then highlight reasons why a mechanism may not be widely used. In the conclusions we mention that CSP is one of the few that has been published and is used.

It is true that if programmers use secure coding practices like prepared statements, then SQLi protections aren't required. However, that may not happen, and this motivates proposals like SQLrand, which might be easier to retrofit in existing codebases.

Our model covers attacks that utilize DSLs in general, and in our categorization there are more than one countermeasures that protect from XPathi.

@@

Rev3:

Sensitivity and specificity could be expressed in terms of a conditional probability---we'll include this in the paper.

P.2 and p.13 highlight that we cannot perform a set of measurements, calculate sensitivity and specificity, and then using {True|False} {Positives|Negatives}, calculate PPV and NPV from equations 3 and 4 directly. One has to go instead through equations 5 and 6.

@@

The comment on the skewed data is valid. We don't know in the papers we studied if test data were skewed. We do find, though, that: more tests could have been performed (Table I and VII.A) and the means to conduct tests should be made available to third parties (Table II and VII.B).

Rev4:

We don't intend to criticize the lack of testing in etiological mechanisms. We attempt to explore why such mechanisms aren't widely used, and suggest that this is one reason.

About demanding prevalence: it may be unfair to ask researchers to provide PPV and NPV values for their mechanisms. In p.13 we explore what this would require---we'll elaborate.

### 2015-01-17 docs/rebuttal_merged.txt

We thank the reviewers for their insightful comments.

General remarks:

We didn't consider mechanisms that haven't been presented in research papers. We
mention Caja due to its importance.

Although some of the presented works use static/dynamic analysis, we don't
consider the area of static/dynamic analysis for vulnerability detection
(another paper covers it [14]), but focus on protections against attacks that
exploit such vulnerabilities.

We'll address the issues indicated by the reviewers, e.g., the title, the point
where language-protection mechanisms detect an attack, the "ease-of-use"
dimension, the SQLi example, the failure of capturing PHPi in our model and the
model's 1/1.1 notation.

@@

Rev1:

Sensitivity and specificity should be more applicable, but not enough data is
available (see VII.A). The usefulness of such metrics in has been advocated
before (Pfleeger and Pfleeger, "Analyzing Computer Security: A
Threat/Vulnerability/Countermeasure Approach"---will be cited).

The many N/As (especially in Table II) actually highlight the code availability
and accuracy testing issues.

We'll include FlowFox and JSand, the paper presenting IFC in WebKit's
JavaScript-Bytecode, and discuss ADsafe etc. AdSentry, Contego, and JSFlow don't
reach our citation threshold.

@@

Using "security" as a dimension is indeed misleading---we mean
ease-of-circumvention, which is orthogonal to "accuracy". We'll replace it with
a more specific term.

We'll enrich the security discussion. For instance, approaches that provide
systematic arguments on their design's security cannot be circumvented like
heuristic/threshold-based approaches.

@@

Rev2:

The lack of code availability makes performing original tests challenging, which
is one of our findings (VII.B).

We attempt to cover mechanisms and then highlight reasons why they may not be
widely used. In the conclusions we mention that CSP is one of the few that has
been published and is used.

@@

Our model covers attacks that utilize DSLs in general, and in our categorization
there are more than one countermeasures that protect from XPathi.

Rev3:

Sensitivity and specificity could be expressed in terms of a conditional
probability---we'll include this in the paper.

P.2 and p.13 highlight that we cannot perform a set of measurements, calculate
sensitivity and specificity, and then using {True|False} {Positives|Negatives},
calculate PPV and NPV from equations 3+4. One has to go instead through
equations 5+6.

We'll expand on the advantages of PPV and NPV. They answer the question about
trusting a detection result; however, it isn't always possible to get data for
them as we indicate in p.13.

The comment on the skewed data is valid. We don't know in the studied papers
if test data was skewed. We do find, though, that: more tests could have been
performed (Table I and VII.A) and the means to conduct tests should be made
available to third parties (Table II and VII.B).

### 2015-01-17 docs/rebuttal_merged.txt

We thank the reviewers for their insightful comments.

General remarks:

We didn't consider mechanisms that haven't been presented in research papers. We
mention Caja due to its importance.

Although some of the presented works use static/dynamic analysis, we don't
consider the area of vulnerability detection (it's been covered [14]), but focus
on protections against attacks that exploit such vulnerabilities.

@@

We'll address the issues indicated by the reviewers, e.g., the title, the point
where language-protection mechanisms detect an attack, the "ease-of-use"
dimension, the SQLi example, the failure of capturing PHPi in our model and the
model's 1/1.1 notation.

Rev1:

Sensitivity and specificity should be more applicable, but not enough data is
available (see VII.A). Their use has been advocated before ("Analyzing Computer
Security: A Threat/Vulnerability/Countermeasure Approach"---will be cited).

@@

Rev2:

The lack of code availability makes performing original tests challenging, which
is one of our findings (VII.B).

We attempt to cover mechanisms and then highlight reasons why they may not be
widely used. In the conclusions we mention that CSP is one of the few that has
been published and is used.

When programmers use secure coding practices like prepared statements, then SQLi
protections aren't required. However, that may not happen, and this motivates
proposals like SQLrand, which might be easier to retrofit.

@@

Our model covers attacks that utilize DSLs in general, and in our categorization
there are more than one countermeasures that protect from XPathi.

Rev3:

Sensitivity and specificity could be expressed in terms of a conditional
probability---we'll include this in the paper.

P.2 and p.13 highlight that we cannot perform a set of measurements, calculate
sensitivity and specificity, and then using {True|False} {Positives|Negatives},
calculate PPV and NPV from equations 3&4. One has to go instead through
equations 5&6.

@@

We'll expand on the advantages of PPV and NPV. They answer the question about
trusting a detection result; however, it isn't always possible to get data for
them as we indicate in p.13.

The comment on the skewed data is valid. We don't know if data was skewed but we
find, that: more tests could have been performed (Table I and VII.A) and testbed
details should be available (Table II and VII.B).

@@

Rev4:

We don't intend to criticize the lack of testing in etiological mechanisms. We
attempt to explore why such mechanisms aren't used, and suggest that this is one
reason.

About demanding prevalence: it may be unfair to ask researchers to provide PPV
and NPV values. In p.13 we explore what this would require---we'll elaborate.

### 2016-02-25 docs/Oakland Paper, Reviews and Rebuttal/rebuttal_merged.txt

We thank the reviewers for their insightful comments.

General remarks:

We didn't consider mechanisms that haven't been presented in research papers. We
mention Caja due to its importance.

Although some of the presented works use static/dynamic analysis, we don't
consider the area of vulnerability detection (covered before [14]), but focus
on protections against attacks that exploit such vulnerabilities.

We'll address the issues indicated by the reviewers, e.g., the title, the point
where language-protection mechanisms detect attacks, the "ease-of-use"
dimension, the SQLi example, the failure of capturing PHPi in our model and the
model's 1/1.1 notation.

@@

Rev1:

Sensitivity and specificity should be more applicable, but not enough data is
available (see VII.A). Their use has been advocated before (Pfleeger and Pfleeger,
"Analyzing Computer Security:A Threat/Vulnerability/Countermeasure Approach"---will
be cited).
